---
title: "Data_Visualization"
output: html_document
date: "2023-03-13"
---

```{r steup, message=FALSE}
library(tidyverse)
library(ggridges)
```


## load weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Scatterplots

```{r}
ggplot(weather_df,aes(x = tmin, y = tmax)) +
  geom_point()
```

New approach, same plot

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Save and edit a plot object

```{r}
weather_plot = weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced Scatterplot

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() + 
  geom_smooth(se = FALSE)
```

what about the aes placement 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) + 
  geom_smooth(se = FALSE)
```

Let's facet some things!!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

  facet_grid(. ~ name) row first then column
  
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() + 
  geom_smooth(se = FALSE) +
  facet_grid(name ~ .)
```

alpha transpirency 
size line 

New graph for temp and date
LOOK THIS!!!!!!!!!!! 
size to certain variable
color to seprerate variable

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .2) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

## neat geom

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_hex()
```
## Univariate plots

Histogram

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

add color 

use fill not color
use dodge for full comp
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram(position = "dodge") 
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() +
  facet_grid(. ~ name)
```

use density for smooth histogram

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3)
```

Box Plot

can give x as categorical variable 

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot()
```

Trendy plots, like a box plot

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name, alpha = .4)) +
  geom_violin() +
  stat_summary(fun = "median")
```

Ridge plots

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges2()
```




